---
title: "Letterboxd Stats"
author: "by Yanto Christoffel"
output: html_document
---

<style type="text/css">

h1.title {
    font-size: 38px;
    font-family: "Liberation Serif";
    color: Black;
    text-align: center;
}
h4.author {
    font-size: 18px;
    font-family: "Liberation Serif";
    font-style: italic;
    color: Black;
    text-align: center;
}

</style>

<center>

```{r, TODO, echo=F, message=F, warning=F}
# TODO: - Tags Over Time plot (with menu to select tags)
#       - Ratings Over Time plot (with menu to select ratings)
#       - Release Years bar plot

# TODO: - Create sections and make a table of contents for them (using toc:true)
#       - Use the watchlist.csv
#       - Make the Last Entry labels for the other timelines in the Over Time plots
```

```{r, System-Settings, echo=F, message=F, warning=F, results='hide'}
# Set the time display to English
Sys.setlocale("LC_TIME", 'en_GB.UTF-8')
```

```{r Loading-Packages, echo=F, message=FALSE, warning=FALSE}
# Check if any required packages are uninstalled
list.of.packages <- c("ggplot2", "plotly", "gridExtra", "ggforce", "rvest")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

# If so, install them
if(length(new.packages)) install.packages(new.packages)

# Load the required packages
for (pkg in list.of.packages) {
    library(pkg, character.only=T)
}
```

```{r, Making-Functions, echo=F, message=F, warning=F}
# Plots a ggplot object and makes it interactive
my_plot_func <-
    function(plot) {
        ggplotly(plot, tooltip="text") %>%
            config(displayModeBar=F) %>%
            layout(hoverlabel=list(align="left",
                                   bgcolor="black"),
                   showlegend=F,
                   plot_bgcolor=plot_background_color)
    }

# Creates a plot that does not display data
make_null_plot <-
    function(title, xlab, ylab, xbreaks=seq(0, 10)) {
        null_plot <- ggplot() +
                theme_minimal() +
                theme(plot.title=element_text(hjust=.5)) +
                labs(title=title,
                     x=xlab,
                     y=ylab) +
                scale_x_discrete(breaks=factor(xbreaks),
                                 limits=as.character(xbreaks)) +
                scale_y_discrete(breaks=factor(seq(0, 10, 2.5)),
                                 limits=as.character(seq(0, 10, 2.5)))

            return(my_plot_func(null_plot))
    }

# Resets the row numbers of a data frame
reset_rows <-
    function(df) {
        row.names(df) <- NULL
        df$id <- as.numeric(row.names(df))
        return(df)
    }

# Retrieves the Letterboxd username from a URI link
get_username <-
    function(link) {
        html_page <- as.character(read_html(link))

        index_start <- gregexpr(pattern="letterboxd.com/", html_page)[[1]][1] + 15
        index_end <- gregexpr(pattern="/film", html_page)[[1]][1] - 1
        username <- substr(html_page, index_start, index_end)

        return(username)
    }
```

```{r, Transforming-Database, echo=F, message=F, warning=F}
# Load the csv file
diary = read.csv('csv_files/diary.csv', stringsAsFactors=FALSE)

# Edit the columns
diary[diary$Rewatch != 'Yes', 'Rewatch'] <- 'No'
diary[is.na(diary$Rating), 'Rating'] <- -1
diary$Watched.Date <- as.Date(diary$Watched.Date)
diary$Date <- as.Date(diary$Date)
colnames(diary)[which(names(diary) == "Name")] <- "Title"
diary$Title <- factor(diary$Title, levels=rev(unique(diary$Title)))

diary$LogDiff <- diary$Date - diary$Watched.Date
diary$Day <- weekdays(diary$Watched.Date)

# Separate TV shows and shorts from movies using the tags and reset row numbers
tvshows <- reset_rows(diary[grepl("tvshow", diary$Tags),])
shorts <- reset_rows(diary[grepl("short", diary$Tags),])
diary <- reset_rows(diary[!grepl("tvshow|short", diary$Tags),])
```

```{r, Setting-Variables, echo=F, message=F, warning=F}
plot_background_color <- "aliceblue"
username <- get_username(diary[1, "Letterboxd.URI"])
```

```{r, Creating-Timelines, echo=F, message=F, warning=F}
# Get today's date
today <- Sys.Date()

# Create variables for the time sections
one_year_ago <- today - 365
thirty_days_ago <- today - 30
seven_days_ago <- today - 7

# Create data frames for the time sections
one_year_ago_df <- reset_rows(diary[diary$Watched.Date > one_year_ago,])
thirty_days_ago_df <- reset_rows(diary[diary$Watched.Date > thirty_days_ago,])
seven_days_ago_df <- reset_rows(diary[diary$Watched.Date > seven_days_ago,])
```

<!-- Circle Stats -->
# {.tabset}

<hr style="border:1px solid gray"> </hr>

```{r, Circle-Stats-Setup, echo=F, message=F, warning=F}
# A data frame that contains information for the three circles
circles <- data.frame(
    x=c(1, 2.8, 4.6),
    y=1,
    r=1,
    colors=c("#ff6600", "#29db00", "#00b0ff"),
    inner="white",
    titles=c("Movies Logged", "Average Rating", "Rewatches")
)

# original_colors <- c("#ff8000", "#00e054", "#40bcf4")

# Makes three circles that display different statistics
make_circle_stats <-
    function(df, circles) {
        # Obtain the required statistics
        movies_logged <- nrow(df)
        average_rating <- sprintf("%.1f", mean(df[df$Rating!=-1, "Rating"]))
        rewatches <- nrow(df[df$Rewatch=='Yes',])

        # Check if the average rating is NaN
        if (average_rating=="NaN") {
            average_rating <- "-"
        }
        
        # Create the column for the labels
        circles$labels <- c(movies_logged, average_rating, rewatches)

        # Plot the circles with their labels
        ggplot() +
            geom_circle(data=circles, mapping=aes(x0=x, y0=y, r=r, fill=colors, color=colors, alpha=.1)) +
            geom_circle(data=circles, mapping=aes(x0=x, y0=y, r=r/2, fill=inner, color=inner)) +
            geom_text(data=circles, mapping=aes(x=x, y=y), label=circles$labels, size=8) +
            geom_text(data=circles, mapping=aes(x=x, y=y+1.25), label=circles$titles, size=5) +
            scale_fill_identity() +
            scale_color_identity() +
            coord_fixed() +
            theme_void() +
            theme(legend.position="None")
    }
```

## All-Time
```{r, Circle-Stats-All, echo=F, message=F, warning=F}
make_circle_stats(diary, circles)
```

## Past 365 Days
```{r, Circle-Stats-Past-365, echo=F, message=F, warning=F}
make_circle_stats(one_year_ago_df, circles)
```

## Past 30 Days
```{r, Circle-Stats-Past-30, echo=F, message=F, warning=F}
make_circle_stats(thirty_days_ago_df, circles)
```

## Past 7 Days
```{r, Circle Stats-Past-7, echo=F, message=F, warning=F}
make_circle_stats(seven_days_ago_df, circles)
```

<!-- Rating Distributions -->
# {.tabset} 

<hr style="border:1px solid gray"> </hr>

```{r, Ratings-Distribution-Setup, echo=F, message=F, warning=F}
# Specify the colors of the different ratings
ratings_plot_colors <- c("0.5"  = "red",
                         "1"    = "tomato",
                         "1.5"  = "orange",
                         "2"    = "gold",
                         "2.5"  = "yellow",
                         "3"    = "greenyellow",
                         "3.5"  = "green",
                         "4"    = "seagreen1",
                         "4.5"  = "aquamarine",
                         "5"    = "cyan")

# Creates a ratings distribution
make_ratings_distribution <-
    function(df, title) {
        data <- df[df$Rating != -1,]
        
        # Return an empty plot if the data has no rows
        if (nrow(data)==0) {
            return(make_null_plot(title,
                                  "Rating",
                                  "Amount",
                                  seq(0.5, 5, 0.5)))
        }
        
        ratings_plot <- ggplot() +
            geom_col(data=data,
                     mapping=aes(x=as.factor(Rating),
                                 y=1,
                                 fill=as.factor(Rating),
                                 Title=Title,
                                 text=paste0(Title, " (", Year, ")", "\n",
                                            Rating, "\U2605")),
                     color="darkslategray") +
            theme_minimal() +
            theme(plot.title=element_text(hjust=.5)) +
            labs(title=title,
                 x="Rating",
                 y="Amount") +
            scale_x_discrete(breaks=factor(seq(0.5, 5, 0.5)),
                             limits=as.character(seq(0.5, 5, 0.5))) +
            expand_limits(y=10) +
            scale_fill_manual(values=ratings_plot_colors) +
            scale_y_continuous(labels=function(x) x)
        
        return(my_plot_func(ratings_plot))
    }
```

## All-Time
```{r, Ratings-Distribution-All, echo=F, message=F, warning=F}
make_ratings_distribution(diary, "Ratings Distribution (All-Time)")
```

## Past 365 Days
```{r, Ratings-Distribution-Past-365, echo=F, message=F, warning=F}
make_ratings_distribution(one_year_ago_df, "Ratings Distribution (Past 365 Days)")
```

## Past 30 Days
```{r, Ratings-Distribution-Past-30, echo=F, message=F, warning=F}
make_ratings_distribution(thirty_days_ago_df, "Ratings Distribution (Past 30 Days)")
```

## Past 7 Days
```{r, Ratings-Distribution-Past-7, echo=F, message=F, warning=F}
make_ratings_distribution(seven_days_ago_df, "Ratings Distribution (Past 7 Days)")
```

<!-- Over Time Plots -->
# {.tabset}

<hr style="border:1px solid gray"> </hr>

```{r, Over-Time-Setup, echo=F, message=F, warning=F}
# Plots movies over time
make_over_time_plot <-
    function(df, title, last_entry_text=NULL, line=NULL) {
        # Return an empty plot if the data has no rows
        if (nrow(df)==0) {
            return(make_null_plot(title,
                                  "Time",
                                  "Cumulative Amount"))
        }
        
        all_over_time_plot <- ggplot() +
            geom_point(data=df,
                        mapping=aes(x=Watched.Date,
                                    y=id,
                                    text=paste0(Title, " (", Year, ")", "\n",
                                               Watched.Date)),
                        color="hotpink") +
            last_entry_text +
            line +
            theme_minimal() +
            theme(plot.title=element_text(hjust=.5)) +
            labs(title=title,
                 x="Time",
                 y="Cumulative Amount")
        
        return(my_plot_func(all_over_time_plot))
    }

# Create variables for the 'Last Entry' text and line
last <- tail(diary, 1)
txt_pos_x <-last$Watched.Date - 365
txt_pos_y <- last$id
x_offset <- 80

txt_clr <- "black"
line_clr <- "blue"

# Create the text
text1 <- geom_text(label=last$id,
                   aes(x=txt_pos_x, y=txt_pos_y),
                   color=txt_clr)

# Create the line
line1 <- geom_segment(aes(x=txt_pos_x + x_offset,
                          y=txt_pos_y,
                          xend=txt_pos_x + 365,
                          yend=txt_pos_y),
                      alpha=.4,
                      color=line_clr)
```

## All-Time
```{r, Over-Time-All, echo=F, message=F, warning=F}
make_over_time_plot(diary, "Movies over Time (All-Time)", text1, line1)
```

## Past 365 Days
```{r, Over-Time-Past-365, echo=F, message=F, warning=F}
make_over_time_plot(one_year_ago_df, "Movies over Time (Past 365 Days)")
```

## Past 30 Days
```{r, Over-Time-Past-30), echo=F, message=F, warning=F}
make_over_time_plot(thirty_days_ago_df, "Movies over Time (Past 30 Days)")
```

## Past 7 Days
```{r, Over-Time-Past-7), echo=F, message=F, warning=F}
make_over_time_plot(seven_days_ago_df, "Movies over Time (Past 7 Days)")
```

<!-- Weekday Distributions -->
# {.tabset}

<hr style="border:1px solid gray"> </hr>

```{r, Weekday-Distribution-Setup, echo=F, message=F, warning=F}
weekdays_order <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

# Creates a bar plot that shows the distribution of movies over the weekdays
make_weekday_distribution <-
    function(df, title) {
        # Return an empty plot if the data has no rows
        if (nrow(df)==0) {
            return(make_null_plot(title,
                                  "Day",
                                  "Count",
                                  weekdays_order))
        }
        
        weekday_plot <- ggplot() +
            geom_col(data=df,
                     mapping=aes(x=as.factor(Day),
                                 y=1),
                     color="purple",
                     fill="purple") +
            theme_minimal() +
            theme(plot.title=element_text(hjust=.5)) +
            labs(x="Day", y="Count", title=title) +
            scale_x_discrete(limits=weekdays_order)
        
        my_plot_func(weekday_plot)
    }
```

## All-Time
```{r, Weekday-Distribution-All, echo=F, message=F, warning=F}
make_weekday_distribution(diary, "Weekday Distribution (All-Time)")
```

## Past 365 Days
```{r, Weekday-Distribution-Past-365, echo=F, message=F, warning=F}
make_weekday_distribution(one_year_ago_df, "Weekday Distribution (Past 365 Days)")
```

## Past 30 Days
```{r, Weekday-Distribution-Past-30, echo=F, message=F, warning=F}
make_weekday_distribution(thirty_days_ago_df, "Weekday Distribution (Past 30 Days)")
```

## Past 7 Days
```{r, Weekday-Distribution-Past-7, echo=F, message=F, warning=F}
make_weekday_distribution(seven_days_ago_df, "Weekday Distribution (Past 7 Days)")
```

#

<hr style="border:1px solid gray"> </hr>

```{r, The-Five, echo=F, message=F, warning=F}
# Finds the indices of a pattern in a source
find_indices <-
    function(pattern, source) {
        indices <- gregexpr(pattern=pattern, source)[[1]][1:10]
        return(indices)
    }

# Fills a list with sub-strings of a text
fill_list <-
    function(my_list, matches, text, start_offset, end_offset) {
        for (i in seq(1, 10, 2)) {
            start <- matches[i] + start_offset
            end <- matches[i+1] + end_offset
            element <- substr(text, start, end)

            my_list <- append(my_list, element)
        }

        return(my_list)
    }

# Finds the first five poster links in the html text
find_posters <-
    function(poster_list, text) {
        start_indices <- gregexpr(pattern="img src", text)[[1]][1:5] + 9
        end_indices <- gregexpr(pattern="jpg", text)[[1]][1:5] + 2
        
        spl <- strsplit(x=paste(start_indices, end_indices), split=' ')
        
        for (i in 1:5) {
            start <- spl[[i]][1]
            end <- spl[[i]][2]
            link <- substr(text, start, end)
            poster_list <- append(poster_list, link)
        }
        
        return(poster_list)
    }

# Returns columns constructed with help of the other functions
create_column <-
    function(pattern, text, start_offset, end_offset) {
        matches <- find_indices(pattern, text)
        column <- vector("list", 0)
        column <- fill_list(column, matches, text, start_offset, end_offset)
        
        return(column)
    }

rss <- paste0("https://letterboxd.com/", username, "/rss")
page_text <- as.character(read_html(rss))

the_five <- data.frame(matrix(NA, nrow=5, ncol=5))
colnames(the_five) <- c("Title", "Year", "Rating", "Date", "Poster")

the_five$Title <- create_column("filmtitle", page_text, 10, -3)
the_five$Year <- create_column("filmyear", page_text, 9, -3)
the_five$Rating <- create_column("memberrating", page_text, 13, -3)
the_five$Date <- create_column("watcheddate", page_text, 12, -3)
the_five$Poster <- find_posters(vector("list", 0), page_text)

one <- the_five[1,]
two <- the_five[2,]
three <- the_five[3,]
four <- the_five[4,]
five <- the_five[5,]

img_w <- 177
img_h <- img_w * 1.5
```

<h3> Most Recent 5 Watches </h2>

</center>

<p align="left">
    <img src="`r one$Poster`" alt="`r one$Title`" width=`r img_w` height=`r img_h` style="padding: 8px">
    <img src="`r two$Poster`" alt="`r two$Title`" width=`r img_w` height=`r img_h` style="padding: 8px">
    <img src="`r three$Poster`" alt="`r three$Title`" width=`r img_w` height=`r img_h` style="padding: 8px">
    <img src="`r four$Poster`" alt="`r four$Title`" width=`r img_w` height=`r img_h` style="padding: 8px">
    <img src="`r five$Poster`" alt="`r five$Title`" width=`r img_w` height=`r img_h` style="padding: 8px">
</p>

<hr style="border:1px solid gray"> </hr>

```{r, echo=F, message=F, warning=F}


```








